Nodal Discontinuous Galerkin Method for the Euler Equations in GR

### 2018-11-01 Documents/Euler/dgEulerGR.tex
Added section about limiting when q_K<0

>>>>

\subsection{Demanding that $q>0$}

Sometimes it happens that $q\left(\ol{\bU}\right)<0$, so our positivity limiter will fail. To get around this we modify the conserved energy, $\tau$ to demand that $q=\ve$, where $0<\ve\ll1$. The transformation we make is:
\begin{equation}
   \ol{ \tau}\longrightarrow\alpha\,\ol{\tau},\hspace{1em}\alpha>1.
\end{equation}
This modifies the definition of $q\left(\ol{\bU}\right)\equiv q_{K}$ from:
\begin{equation}
   q_{K}=\ol{\tau}+\ol{D}-\sqrt{\ol{D}^{2}+\ol{S}^{2}+\ve}<0,
\end{equation}
to:
\begin{equation}
   \ve=\alpha\,\ol{\tau}+\ol{D}-\sqrt{\ol{D}^{2}+\ol{S}^{2}+\ve}.
\end{equation}
Solving this for $\alpha$, we get:
\begin{equation}
   \alpha=\ol{\tau}^{-1}\left[\ve-\ol{D}+\sqrt{\ol{D}^{2}+\ol{S}^{2}+\ve}\right].
\end{equation}
